### 2024-01-02 tesis_Ashish/Chapter4/chapter4.tex
Sehrawat A thesis 17 Dec 2023
Updated thesis 2 Jan 2024

\item Stability: Systematic uncertainties can be introduced due to time-dependent changes in detector performance and environmental conditions. These changes can be influenced by various factors, including detector aging, radiation damage, and fluctuations in noise. A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig. \ref{fig:stabprof} depicting slight instabilities in PCC luminosity over time.
%Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
Detector aging can result in time-dependent changes in the detector's performance. For example, as the detector ages or sustains radiation damage, its efficiency may decrease, leading to a reduction in the number of detected events for a given luminosity. %This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
Fluctuation in the  noise level in the detector can also fluctuate over time due to changes in the experimental conditions. Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity. Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity. %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
The standard deviation of ratio of luminosity from best and second best luminometer is used as stability systematic uncertainty as shown in Fig. \ref{fig:stabprof1}. The standard deviation provides a measure of the spread or dispersion of the measurements. If the measurements are stable, the spread will be small, and the standard deviation will be low. Conversely, if there are time-dependent changes in the detector performance or environmental conditions, the measurements will vary more, and the standard deviation will be higher.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all_1.png}
\caption[Luminosity Ratio Profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
\label{fig:stabprof1}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5_1.png}
  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity. The residual fraction is given by the ratio of\
 the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch. Right: Type 2 residual as a function of instantane\
ous luminosity. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch. Ra\
ndom trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
  \label{fig:stabprof}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization & Length scale & 0.2  \\
 & Orbit drift &  0.2  \\
 & x-y nonfactorization & 0.6 \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & 0.2 \\
 & Beam current calibration  & 0.2 \\
 & Ghost and satellite & 0.1 \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
 & Background subtraction  & 0.1 \\
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
 & Linearity  & 0.4 \\
Total &  &  1.08 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}

>>>>

\item Stability: Systematic uncertainties can be introduced due to time-dependent changes in detector performance and environmental conditions. These changes can be influenced by various factors, including detector aging, radiation damage, and fluctuations in noise. A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig. \ref{fig:stabprof_7098} depicting slight instabilities in PCC luminosity over time.
%Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
Detector aging can result in time-dependent changes in the detector's performance. For example, as the detector ages or sustains radiation damage, its efficiency may decrease, leading to a reduction in the number of detected events for a given luminosity. %This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
Fluctuation in the  noise level in the detector can also fluctuate over time due to changes in the experimental conditions. Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity. Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity. %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
The standard deviation of ratio of luminosity from best and second best luminometer is used as stability systematic uncertainty as shown in Fig. \ref{fig:stabprof1}. The standard deviation provides a measure of the spread or dispersion of the measurements. If the measurements are stable, the spread will be small, and the standard deviation will be low. Conversely, if there are time-dependent changes in the detector performance or environmental conditions, the measurements will vary more, and the standard deviation will be higher.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all_1.png}
\caption[Luminosity Ratio Profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
\label{fig:stabprof_7098}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5_1.png}
  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity. The residual fraction is given by the ratio of\
 the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch. Right: Type 2 residual as a function of instantane\
ous luminosity. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch. Ra\
ndom trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
  \label{fig:stabprof_4012}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
\label{tab:systematic-uncertainty}
\begin{tabular}{cccc}
  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
\hline
Normalization  Length scale & -  \\
 & Orbit drift &  -  \\
 & x-y nonfactorization & - \\
 & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
 & Beam current calibration  & - \\
 & Ghost and satellite & - \\
 & Scan to scan variation & 0.3 \\
 & Bunch to bunch variation & 0.1 \\
 & Cross detector consistency  & 0.5 \\
 & Background subtraction  & 0.1 \\
Integration & Afterglow  &  0.3 \\
 & Cross detector stability & 0.3 \\
 & Linearity  & 0.4 \\
%Total &  &  1.08 \\
\end{tabular}
%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
\label{tab:systematic-uncertainty}
\end{table}
